```{r}
options(scipen=999)
library(readxl)
library(dplyr)
library(igraph)
library(readr)
```

## Unweighted graph

#### Downloading graph from adjacency matrix
```{r message=FALSE, warning=FALSE}
m <- read_excel("C:/Users/avalu/Desktop/RStudio/Networks/matrix.xlsx",col_names = TRUE)
m <- m %>% dplyr::select(-...1)
rownames(m)<- names(m)
m<- as.matrix.data.frame(m)
UI_graph_unw <- graph_from_adjacency_matrix(adjmatrix = m, mode = "undirected", weighted = NULL)
UI_graph_unw <- simplify(UI_graph_unw)
```

#### Creating dataframe with degree centrality metric
```{r}
for_stata<- as.data.frame(degree(UI_graph_unw))
colnames(for_stata)<-c("degree_unw_total")
for_stata$id<- rownames(for_stata)
rownames(for_stata) <- NULL
```

#### Visualization. Appendix 2
```{r}
library(visNetwork)
universities<- as.vector(for_stata$id[40:60])
companies<-as.vector(for_stata$id[1:39])
for_stata$UI<- c(rep(1,39),rep(2,21)) #Technical variable for visualization
graph<- toVisNetworkData(UI_graph_unw)
graph$nodes$color = c("#330099","orange")[for_stata$UI]
graph$nodes$size = for_stata$degree_unw_total

graph$edges$color<- ifelse((graph$edges$from%in% companies & graph$edges$to%in% companies) ,"#330099",ifelse((graph$edges$from%in%universities & graph$edges$to%in% universities),"orange","green"))
graph$edgeswidth<- 3
visNetwork(nodes = graph$nodes, edges = graph$edges, height = "2400px", width = "2400px") %>%  visIgraphLayout(type="full", smooth=TRUE,layout = "layout_nicely")
```

## Weighted graph. Weight - number of joint publications

#### Downloading graph from adjacency matrix
```{r}
UI_graph_w <- graph_from_adjacency_matrix(adjmatrix = m, mode = "undirected", weighted = TRUE)
UI_graph_w <- simplify(UI_graph_w)
```

#### Adding eigen centrality metric to dataset
```{r}
x<- eigen_centrality(UI_graph_w,directed = FALSE,weights = NULL,scale=FALSE)
for_stata$eigen_w_unscaled<- as.numeric(x$vector)
```

#### Visualization. Appendix 3
```{r}
graph2<- toVisNetworkData(UI_graph_w)
graph2$nodes$color = c("#330099","orange")[for_stata$UI]
graph2$nodes$size = for_stata$degree_unw_total
graph2$edges$color<- ifelse((graph$edges$from%in% companies & graph$edges$to%in% companies) ,"#330099",ifelse((graph$edges$from%in%universities & graph$edges$to%in% universities),"orange","green"))
graph2$edges$width<- E(UI_graph_w)$weight/10
visNetwork(nodes = graph2$nodes, edges = graph2$edges, height = "2400px", width = "2400px") %>% 
  visIgraphLayout(type="full", smooth=TRUE,layout = "layout_nicely")
```

#### Change weights to inverse value. For betweennees the weight is considered as "distance between two nodes". If weight is 1/number of joint publications we obtain the situation when the more publications the closer the nodes. 
```{r}
E(UI_graph_w)$weight<- 1/E(UI_graph_w)$weight
```

#### Adding betweenness metric to dataset
```{r}
for_stata$betweenness_w_total<- betweenness(UI_graph_w)
```

## Saving the required centality metrics to csv
```{r}
for_stata %>% select(-UI) %>% write_csv("for_stata.csv")
```

